\section{Objectives of the Project}

\subsection{Industry Objectives}
What goals can be achieved in the industry through this project

This is a tool from developers to developers. Here are some of the industrial objectives that can be achieved via this project:

It will save the company's time. A lot of the time, all these configurations and set ups take up more than an hour. With this tool, the developers would easily be able to set up everything via a single command.
This tool will enhance the productivity of developers. They will not be copying the same code and doing the same configurations over and over again.

\subsection{Research Objectives}
How can this project enhance current research

Since a lot of boilerplate code exists only to the extent of their technology, there is not yet a proper tool in the market that is generic enough. This provides a huge research opportunity to see if developers will adopt this tool or not.

The current research is only limited to individual tools. This tool will provide a wider pool for research because of its general nature.

\subsection{Academic Objectives}
How does this project benefit you knowledge wise

The implementation of such a tool will require us to study different web frameworks and languages, how they implement certain generic features, etc. We will also be required to think of techniques to make the implementation of the codebase of this tool as generic as possible. And all this will require us to understand and learn different web frameworks to the point that we can build small applications in them.
